\LARGE \bf Matrix Multiplication-Driven Repulsive Fields for 3D Voxel-Based TSDF Calculation

### 2024-03-15 Articles/IROS/root.tex
second draft results

\begin{equation}
	\dot{q}_{rep} = \sum_{i=1}^{K} \alpha_i J_{d_i}^{+} \left(v_i - J_{d_i} J^{+} \xi_{p} \vec{v}_{att}\right)
\end{equation}

@@

In the first case (Fig. \ref{fig:keyframes-3d-column}, \ref{fig:plots-3d-column}), the manipulator safely 'curls' or selects a path to a point located on the other side of a column, avoiding the obstacle with the potential field calculated by the proposed method. The constants chosen for the primary task are \( k_v = 5 \) and \( k_w = 20 \). The weighting constants for the individual POIs are \( \alpha = \frac{[ \frac{3}{9}, \frac{2}{9}, \frac{1}{9}, \frac{1}{9}, \frac{1}{9}, \frac{1}{9} ]}{10} \), where the biggest weight belongs to the point on the manipulator which is closest to the obstacle and so on. As the most direct path for the end-effector to the target passes straight through the column, an approach that would result in a collision, we implement a reduction of the primary speed in the vicinity of the obstacle, setting \( \xi_{p} = 1 \). The simulation is performed for 50 steps.

@@

%\begin{figure}
%	\centering
%	\includegraphics[width=1\linewidth]{keyframes_2D_a.eps} % Replace 'example-image' with the filename of your image
%	\caption{Example Image}
%	\label{fig:keyframes-2d-column}
%\end{figure}
%
%\begin{figure}
%	\centering
%	\includegraphics[width=1\linewidth]{keyframes_2_columns.eps} % Replace 'example-image' with the filename of your image
%	\caption{Example Image}
%	\label{fig:keyframes-2-column}
%\end{figure}
%
%
%\add{EXAMPLE: MANIPULATOR AND MOVING NOISY BALL}
%
%\begin{figure}
%	\centering
%	\includegraphics[width=1\linewidth]{keyframes_3D_ball.eps} % Replace 'example-image' with the filename of your image
%	\caption{Example Image}
%	\label{fig:keyframes-3d-ball}
%\end{figure}
%
%\begin{figure}
%	\centering
%	\includegraphics[width=1\linewidth]{keyframes_2D_ball.eps} % Replace 'example-image' with the filename of your image
%	\caption{Example Image}
%	\label{fig:keyframes-2d-ball}
%\end{figure}
%
%\begin{figure}
%	\centering
%	\includegraphics[width=0.75\linewidth]{keyframes_2_columns_ball.eps} % Replace 'example-image' with the filename of your image
%	\caption{Example Image}
%	\label{fig:keyframes-2-column-ball}
%\end{figure}
%

@@

>>>>

\begin{equation}
	\dot{q}_{rep} = k_r \sum_{i=1}^{K} \alpha_i J_{d_i}^{+} \left(v_i - J_{d_i} J^{+} \xi_{p} \vec{v}_{att}\right)
\end{equation}

@@

In the first case (Fig. \ref{fig:keyframes-3d-column}, \ref{fig:plots-3d-column}), the manipulator safely 'curls' or selects a path to a point located on the other side of a column, avoiding the obstacle with the potential field calculated by the proposed method. The constants chosen for the primary task are \( k_v = 5 \) and \( k_w = 1.5 \), for the avoidance task \(k_r=20\). The weighting constants for the individual POIs are \( \alpha = \frac{[ \frac{3}{9}, \frac{2}{9}, \frac{1}{9}, \frac{1}{9}, \frac{1}{9}, \frac{1}{9} ]}{10} \), where the biggest weight belongs to the point on the manipulator which is closest to the obstacle and so on. As the most direct path for the end-effector to the target passes straight through the column, an approach that would result in a collision, we implement a reduction of the primary speed in the vicinity of the obstacle, setting \( \xi_{p} = 1 \). The simulation is performed for 50 steps.

@@

%V drugem primeru (Fig. \ref{fig:keyframes-3d-ball}, \ref{fig:plots-ball}) se naš robot giblje v dinamične okolju. Predlagan način izračuna odbojnih hitrosti je dobra izbira v primeru, ko potrebujemo lokalno optimizacijsko metodo za upoštevanje dinamičnih spremeb. V izbranem primeru imamo žogo, ki se med potekom optimizacije enakomerno premika iz leve strani grafa proti desni strani (torej v smeri y osi od 0.4 v trenutku 0 do 1.4 v zadnjem koraku simulacije). Primarna naloga ima sedaj nalogo vzdrževati vrh robota v eni točki, pri čemer smo za večjo sposobnost izogibanja oviri zanemarili izbiro orientacije vrha EE. To nam poveča sposobnost gibanja, posledično ne potrebujemo primary speed task slowdown  \( \xi_{p} = 0 \). The constants chosen for the primary task are \( k_v = 2 \) and \( k_w = 0 \), for the avoidance task \(k_r=3\). The weighting constants for the individual POIs are \( \alpha = \frac{[ \frac{1}{5}, \frac{1}{5}, \frac{1}{5}, \frac{1}{5}, \frac{1}{5}, \frac{1}{5} ]}{10} \).

In the second scenario (Fig. \ref{fig:keyframes-3d-ball}, \ref{fig:plots-ball}), our robot operates within a dynamic environment. The proposed method for calculating repulsive velocities proves to be a suitable choice when a local optimization approach is needed to accommodate dynamic changes. In this scenario, a ball moves consistently from the left to the right side of the graph (i.e., along the y-axis from 0.4 at the initial moment to 1.4 in the final step of the simulation), as governed by the equation \( y_{\text{ball}} = 0.4 + (1.4 - 0.4) \times \frac{N_{\text{step}}}{75} \),  with \( x_{\text{ball}} = 1.25 \) and \( z_{\text{ball}} = 0.7 \). The primary task is now to maintain the robot's end-effector (EE) at a fixed point, disregarding EE orientation to enhance obstacle avoidance capability. This increases maneuverability, thereby eliminating the need for primary speed task slowdown (\( \xi_{p} = 0 \)). Constants selected for the primary task are \( k_v = 2 \) and \( k_w = 0 \), and for the avoidance task \( k_r = 3 \). Weighting constants for the individual POIs are \( \alpha = \frac{[ \frac{1}{5}, \frac{1}{5}, \frac{1}{5}, \frac{1}{5}, \frac{1}{5}, \frac{1}{5} ]}{10} \). The simulation is performed for 75 steps.

%\begin{figure}
%	\centering
%	\includegraphics[width=1\linewidth]{keyframes_2D_a.eps} % Replace 'example-image' with the filename of your image
%	\caption{Example Image}
%	\label{fig:keyframes-2d-column}
%\end{figure}
%
%\begin{figure}
%	\centering
%	\includegraphics[width=1\linewidth]{keyframes_2_columns.eps} % Replace 'example-image' with the filename of your image
%	\caption{Example Image}
%	\label{fig:keyframes-2-column}
%\end{figure}
%
%
%\add{EXAMPLE: MANIPULATOR AND MOVING NOISY BALL}
%
\begin{figure}
	\centering
	\includegraphics[width=1\linewidth]{keyframes_2D_ball.eps} % Replace 'example-image' with the filename of your image
	\caption{Dynamic obstacle avoidance scenario: Sequential keyframes illustrating the robot’s maneuvering in response to a progressively moving ball from left to right across the workspace.}
	\label{fig:keyframes-3d-ball}
\end{figure}
%
%\begin{figure}
%	\centering
%	\includegraphics[width=1\linewidth]{keyframes_2D_ball.eps} % Replace 'example-image' with the filename of your image
%	\caption{Example Image}
%	\label{fig:keyframes-2d-ball}
%\end{figure}
%
\begin{figure}
	\centering
	\includegraphics[width=1\linewidth]{4plots_ball.eps} % Replace 'example-image' with the filename of your image
	\caption{Performance in a dynamic obstacle avoidance scenario: (a) Primary Task error (b) Joint Velocities $\dot{\theta}$, (c) Joint Positions $\theta$, and (d) Norms of Repulsive Velocities $v_{rep}$.}
	\label{fig:plots-ball}
\end{figure}
%

@@

\add{TODO}
